Setting up Data

### 2020-05-08 src/SetupData.Rmd
saving while debugginh
formating the setupData files

---
title: "Setting up Data"
author: "April Peterson"
date: "`r format(Sys.time(), '%d %B %Y')`"
output: html_document
---

@@

@@

- rm all of BD data?

@@

```{r setup, include=FALSE}
library(plyr)
library(dplyr)
library(raster)#for cV
library(ggplot2)
library(knitr)
library(kableExtra)
library(here)

#knitr::opts_chunk$set(echo = FALSE)

@@

meta.data = read.csv(here("data", "/clean.Meta.Data.txt"),sep = "\t", header=TRUE)

#remove all MAD (peromyscus) from meta.data
meta.data <- meta.data[ !grepl("MAD", meta.data$mouse) , ]

MLH1_data = read.csv(here("data", "/AnonData_formated.csv"), header=TRUE)

@@

@@

original_DF = MLH1_data
original_DF$fileName <- (original_DF$Original.Name)

source("~./MLH1repo/src/CommonFunc_MLH1repo.R")
original_DF <- add_mouse(original_DF)
original_DF <- add_strain(original_DF)
original_DF <- add_category(original_DF)
original_DF <- add_sex(original_DF)

#check for duplicated data, make duplicated data DF for repeatability
#anyDuplicated(original_DF$fileName)#219
#orig_DF <- original_DF[duplicated(original_DF$Original.Name),]
#these just produce 1 set of the duplicated

#isolate the duplicates (fileName) from main MLH1 DFs
n_occur <- data.frame(table(original_DF$fileName))
#n_occur[n_occur$Freq > 1,] displays the dups
original_DF_duplicates <- original_DF[original_DF$fileName %in% n_occur$Var1[n_occur$Freq > 1],]#2 is the max freq of duplicates, 
#use the above DF for quantifying repeatability in the Main_report.Rmd
#duplicates are cells counted twice

#are there duplicated filenames+batch
original_DF_duplicates$unique.key <-  paste(original_DF_duplicates$fileName, original_DF_duplicates$Batch, sep = "_")
#anyDuplicated(original_DF_duplicates$unique.key)#31 duplicated fileName_batch ... really 2?

@@

source("~./MLH1repo/src/CommonFunc_MLH1repo.R")

@@

MLH1_data <- add_mouse(MLH1_data)
MLH1_data <- add_category(MLH1_data)
MLH1_data <- add_strain(MLH1_data)
MLH1_data <- add_sex(MLH1_data)
MLH1_data <- add_subsp(MLH1_data)
#add species
MLH1_data <- add_species(MLH1_data)
```

@@

#show_col(hue_pal()(5))

#add Rec group,

#Curated_BivData$Rec.group <- ifelse(grepl("PWD male", Curated_BivData$category), 1, 
#                              ifelse(grepl("MSM male", Curated_BivData$category), 1,
#                                ifelse(grepl("SKIVE male", Curated_BivData$category), 1, 0)))

#Curated_BivData$Rec.group_alt <- ifelse(grepl("PWD male", Curated_BivData$category), 1, 
#                              ifelse(grepl("MSM male", Curated_BivData$category), 1, 0))
```

@@

save.image("~./MLH1repo/data/MLH1/MLH1_data_setup_4.26.20.RData")

>>>>

---
title: "Setting up Data"
author: "April Peterson"
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  html_document: default
  pdf_document: default
---

@@

- try calq correlation of MLH1 counts across duplicates

@@

@@

```{r setup, include=FALSE}
library(plyr)
library(dplyr)
library(raster)#for cV
library(ggplot2)
library(knitr)
library(kableExtra)
library(here)
library(xlsx)
#knitr::opts_chunk$set(echo = FALSE)

@@

meta.data = read.csv(here("data", "/clean.Meta.Data.txt"), sep = "\t", header=TRUE)
#remove all MAD (peromyscus) from meta.data
#meta.data <- meta.data[ !grepl("MAD", meta.data$mouse) , ]

@@

#MLH1_data = read.csv(here("data", "/AnonData.csv"), sep="\t", header=TRUE)
#read.csv was breaking things
MLH1_data = read.xlsx2(here("data", "/AnonData_formated.xlsx"), header=TRUE, 1)

#formating the original anon file
#MLH1_data = read.xlsx2(here("data", "/AnonData.xlsx"), header=TRUE, 1)
#MLH1_data$fileName <- (MLH1_data$Original.Name)

#MLH1_data <- add_mouse(MLH1_data)
#MLH1_data <- add_category(MLH1_data)
#MLH1_data <- add_strain(MLH1_data)
#MLH1_data <- add_sex(MLH1_data)
#MLH1_data <- add_subsp(MLH1_data)
#MLH1_data <- add_species(MLH1_data)
#write csv to MLH1 file
#write.xlsx2(MLH1_data, "AnonData_formated.xlsx", sheetName="Sheet1",
#  col.names=TRUE, row.names=FALSE, append=FALSE)
```

original_DF = MLH1_data

#isolate the duplicates (fileName) from main MLH1 DFs
n_occur <- data.frame(table(original_DF$fileName))
#n_occur[n_occur$Freq > 1,] displays the dups
original_DF_duplicates <- original_DF[original_DF$fileName %in% n_occur$Var1[n_occur$Freq > 1],]#2 is the max freq of duplicates,

#use the above DF for quantifying repeatability in the Main_report.Rmd
#duplicates are cells counted twice

#are there duplicated filenames+batch
original_DF_duplicates$unique.key <-  paste(original_DF_duplicates$fileName, original_DF_duplicates$Batch, sep = "_")

anyDuplicated(original_DF_duplicates$unique.key)#31 duplicated fileName_batch and batch number --

#calculate the correlation across duplicates. First issue is to match up and organize the matching 
#for each fileName - make cols, for MLH1-1 and MLH1-2
#remove Xs, for fileName with 
original_DF_duplicates <- original_DF_duplicates[!grepl("X", original_DF_duplicates$X),]
#make a new DF -- with one fileName and the MLH1-1 and MLH1-2
#  (duplicate / dostinct fileName )

#keep just 1 of duplicates from MLH1_data
#MLH1_data <- MLH1_data[duplicated(MLH1_data$fileName),]
MLH1_data <- MLH1_data %>% distinct(fileName, .keep_all = TRUE)

@@

`r length(original_DF_duplicates$Random.Name)` rows are marked as duplicate.

@@

@@

@@

@@

save.image("~./MLH1repo/data/MLH1/MLH1_data_setup_5.5.20.RData")
